Software Citation Principles

### 2016-04-18 sc-principles/software-citation-principles.tex
fixing bib entry

While not usually expressed as software citation principles, a number of groups
have developed community guidelines around software and data citation. Van de
Sompel et al.~\cite{VandeSompel2004} argue for registration of all units of
scholarly communication, including software. In ``Publish or be damned? An
alternative impact manifesto for research
software''~\cite{ssi-publish-or-be-damned}, Chue Hong lists nine principles as
part of ``The Research Software Impact Manifesto.'' In the
``Science Code Manifesto'`~\cite{sciencecodemanifesto}, the founding signatories
cite five core principles (Code, Copyright, Citation, Credit, Curation) for
scientific software.

>>>>

While not usually expressed as software citation principles, a number of groups
have developed community guidelines around software and data citation. Van de
Sompel et al.~\cite{VandeSompel2004} argue for registration of all units of
scholarly communication, including software. In ``Publish or be damned? An
alternative impact manifesto for research
software''~\cite{ssi-publish-or-be-damned}, Chue Hong lists nine principles as
part of ``The Research Software Impact Manifesto.'' In the
``Science Code Manifesto''~\cite{sciencecodemanifesto}, the founding signatories
cite five core principles (Code, Copyright, Citation, Credit, Curation) for
scientific software.
